### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
adding Eddie's comments
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

We thank you for asking us to comply with the Referees' reports. We are submitting the revised version of our paper entitled as ``{\em ESBMC-GPU A Context-Bounded Model Checking Tool to Verify CUDA Programs},'' by Felipe R. Monteiro, Erickson H. da S. Alves, Isabela S. Silva, Hussama A. Ismail, Lucas C. Cordeiro, and Eddie B. de Lima Filho.

@@

We hope that these revisions in the manuscript and our responses will be sufficient to make our manuscript suitable for publication in the Journal of Science of Computer Programming (Software Track).

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} We really appreciate the reviewer's summary about our work, which fairly describes the main contributions of our manuscript. We also appreciate the reviewer's comments and also his/her effort to provide relevant comments to improve our paper. We have carefully revised our manuscript, considering all valuable and constructive comments/suggestions.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: haven't we explained that in {\bf Limitations} subsection on page 6?} The reviewer wants to know more details about the type of bugs that we have found in the benchmarks. May I ask you to take a look at our journal paper? I think we describe the type of bugs there. }
\end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Hussama: could you answer this question? I believe we need the list of properties that each tool can verify and then we can see the differences between them. We should display such information on the website, in addition to the manuscript.}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: you have more experience with the experimental evaluation. What do you think?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: would you be able to tell me that?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: any insights about coverage?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: I didn't get it. Did you? Can you cite our TACAS 2014 paper? I suggest you to read that paper which briefly explains our memory model. Then you can properly reply to the reviewer and cite that paper.}}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:}}
\end{quote}

>>>>

We thank you for asking us to comply with the Referees' reports, which allowed us to submit a revised version of our paper, entitled as ``{\em ESBMC-GPU A Context-Bounded Model Checking Tool to Verify CUDA Programs},'' by Felipe R. Monteiro, Erickson H. da S. Alves, Isabela S. Silva, Hussama A. Ismail, Lucas C. Cordeiro, and Eddie B. de Lima Filho.

@@

We hope that those revisions in the manuscript and our responses will be sufficient to make our manuscript suitable for publication in the Journal of Science of Computer Programming (Software Track).

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} We really appreciate the reviewer's summary about our work, which fairly describes its main contributions. We also appreciate the reviewer's comments and also his/her effort to provide a relevant discussion, with the goal of improving our paper. As a consequence, we have carefully revised our manuscript, considering all suggestions.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: haven't we explained that in {\bf Limitations} subsection on page 6?} \textcolor{green}{Eddie: It seems he meant a detailed explanation about each bug. Do you remember what we did in our former articles? We described each benchmark, which included clarifications about existing bugs... We did not do that here... We only said ``covers basic functions commonly used by real CUDA applications'', but we did not clearly showed what... Maybe a brief explanation of each pat of our test set...} The reviewer wants to know more details about the type of bugs that we have found in the benchmarks. May I ask you to take a look at our journal paper? I think we describe the type of bugs there. }
\end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Hussama: could you answer this question? I believe we need the list of properties that each tool can verify and then we can see the differences between them. We should display such information on the website, in addition to the manuscript.}\textcolor{green}{Eddie: We only do that for our approach (a brief discussion), at the beginning of page 6, above section performance... We need to do that for the other tools... Do we have room for that?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: you have more experience with the experimental evaluation. What do you think?}\textcolor{green}{Eddie: Maybe, the comment above answers that}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: would you be able to tell me that?} \textcolor{green}{Eddie: A simple paragraph, just commenting on that and preferably giving a percentage...}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: any insights about coverage?} \textcolor{green}{Eddie: A simple text, just commenting on that and preferably giving a percentage...}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: I didn't get it. Did you? Can you cite our TACAS 2014 paper? I suggest you to read that paper which briefly explains our memory model. Then you can properly reply to the reviewer and cite that paper.}\textcolor{green}{Eddie: Maybe he is talking about shared, register, global and local... We need to show that our memory model correctly represent such types...}}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:}\textcolor{green}{Eddie: We have to comment on kernels, blocks and threads, in order to clarify that, showing that it it feasible ...}}
\end{quote}
